\documentclass{article}
\usepackage[utf8]{inputenc}

\title{uganda\_gwas}
\author{Tommy Carstensen}
\date{December 2014}

\begin{document}

\maketitle

\section{Sample Collection, Library Preparation and DNA Sequencing}
Blood samples were collected. Sequencing of 5000 samples was carried out on Illumina HiSeq 2000 machines to a an average depth of coverage of 4x. 14 samples were excluded during QC prior to pre-processing of the sequencing reads.
%APP5293638
%APP5292945
%APP5340012
%APP5340572
%APP5340400
%APP5340834
%APP5340801
%APP5340217
%APP5341239
%APP5341735
%APP5341575
%APP5341180
%APP5341162
%APP5341189

\section{Pre-Processing of Reads}
The reads were aligned to build 37 of the human reference sequence with decoys (hs37d5) using BWA version ?.?. Reads with an inferior mapping quality are ignored (--min_mapping_quality_score 20) during variant calling. To improve the accuracy of downstream processing steps we realigned around INDELs using GATK RealignerTargetCreater and GATK IndelRealigner.
%figure with mapped reads, coverage, heterozygosity, etc.?

\section{Variant Calling}
Variant calling was performed with GATK HaplotypeCaller 3.2. Each sample was downsampled to a maximum coverage of 250 during variant calling (--downsampling_type BY_SAMPLE --downsample_to_coverage 250). Reads with an inferior mapping quality were ignored (--min_mapping_quality_score 20). The minimum base quality required to consider a base for calling was set to 10 (--min_base_quality_score 10). No more than 6 alternate alleles were emitted at each site (--max_alternate_alleles 6). In an attempt to provide better input for the subsequent variant filtering step variants of inferior quality were not called  (--standard_min_confidence_threshold_for_calling 10 and --standard_min_confidence_threshold_for_emitting 10).

\section{Variant Filtering}

\section{Refinement}
Genotype probablities were refined with BEAGLE4 (rxxx?) in the absence of a reference panel. After refinement only biallelic SNPs matching those in the Illumina Omni2.5 dataset after quality control were brought forward for analysis; i.e. xxx,xxx biallelic SNPs. After refinement samples with high heterozygosity were removed.

\end{document}
